Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities

### 2020-12-23 docs/manuscript/main.tex
abstract is 200words docs/manuscript/main.tex

\begin{abstract}
Human movement variability arises from the process of 
mastering redundant (bio)mechanical degrees of freedom (DOF)
to successfully accomplish any given motor task
(from the most complex to even the simplest one) 
where flexibility and stability of many possible joint 
combinations helps to adapt to environment conditions. 
While the analysis of movement of variability is becoming increasingly 
popular as a diagnostic tool or skill performance evaluation, 
there are remain challenges in terms of defining 
the most appropriate methods and parameters to apply. 
For this work, we therefore investigate nonlinear dynamics methods 
such as reconstructed state space (RSSs), uniform time-delay embedding, 
recurrence plots (RPs) and recurrence quantification analysis metrics (RQAs)
with real-world time-series data of wearable inertial sensors. 
That said, twenty right-handed healthy participants 
imitated simple vertical and horizontal arm movements in normal 
and faster velocity from an humanoid robot.
We applied nonlinear methods to four activities, 
four window lengths and three levels of smoothed time-series data,
to then found visual differences in the patterns of RSSs and RPs
and statistical differences with RQA metrics.
We therefore conclude that Shannon Entropy for RQA is a robust method 
that help us to quantify activities, types of sensors, windows lengths 
and level of smoothness.
Hence this work might enhance the development of 
better diagnostic tools for applications in 
rehabilitation and sport science for skill performance
or new forms of human-humanoid interaction for
quantification of movement adaptations and motor pathologies.
\end{abstract}

>>>>

\begin{abstract}
Human movement variability arises from the process of 
mastering redundant (bio)mechanical degrees of freedom
to successfully accomplish any given motor task
where flexibility and stability of many possible joint 
combinations helps to adapt to environment conditions. 
While the analysis of movement of variability is becoming increasingly 
popular as a diagnostic tool or skill performance evaluation, 
there are remain challenges on applying the most appropriate methods. 
We therefore investigate nonlinear methods 
such as reconstructed state space (RSSs), uniform time-delay embedding, 
recurrence plots (RPs) and recurrence quantification analysis (RQAs)
with real-world time-series data of wearable inertial sensors. 
That said, twenty healthy participants 
imitated vertical and horizontal arm movements in normal 
and faster velocity from an humanoid robot.
We applied nonlinear methods to the collected data 
to found visual differences in the patterns of RSSs and RPs
and statistical differences with RQAs.
We conclude that Shannon Entropy with RQA is a robust method 
that helps to quantify activities, types of sensors, windows lengths 
and level of smoothness.
Hence this work might enhance the development of 
better diagnostic tools for applications in 
rehabilitation and sport science for skill performance
or new forms of human-humanoid interaction for
quantification of movement adaptations and motor pathologies.
\end{abstract}
